Competing Bandits: The Perils of Exploration under Competition

### 2018-09-02 paper/content/inverted_u.tex
add back steven's changes

\documentclass[../competing_bandits.tex]{subfiles}
\begin{document}

\section{Competition vs Better Algorithms}\label{section:5}
\swedit{how about just name the section ``inverted U''?}  \swedit{Now
  we demonstrate the inverted-U relationship between the incentivized
  algorithms and the competition levels. In particular, we investigate
  the incentivized algorithms under three different regimes: permanent
  monopoly, temporary monopoly, and permanent duopoly. First, the
  story for permanent monopoly is relatively straightforward.}

\OMIT{main results that can be summarized via the empirically documented inverted-U relationship between competition and innovation described in \cite{Aghion-QJE05}. 
}

\OMIT{
\begin{finding}
\textit{For sufficiently low warm start, the optimal strategies in the competition game are:
\begin{center}
\textbf{Permanent Monopoly} - $\DG$ \\
\textbf{Temporary Monopoly} - $\TS$ \\
\textbf{Permanent Duopoly} - $\DG$ \\
\end{center}
The conditions on $\TS$ being dominant under the temporary monopoly are that the incumbent is a temporary monopoly for sufficiently many periods.
}
\end{finding}
}

@@

@@

\OMIT{
\begin{definition}
\textit{Effective End of Game (EEOG)} - the last round, $t$, in a simulation where the agent alive at $t-1$ and the agent alive at $t$ choose different firms.
\end{definition}
}

Since both firms enter at the same time the game is symmetric and we only need to compute the payoffs of three pairs of strategies. We do not report them in the figures, but when both firms play the same algorithm the expected market share is 50/50.

@@

\textbf{Temporary Monopoly} We now consider asymmetries in the timing of entry so that one firm enters the market before the other and serves as a monopolist in the periods until the other firm enters. In terms of our model, this corresponds to varying the value of $X$. For this section we report results fixing $T_0 = 20$ and focus on the family of instances where we observed that, for this warm start, $\DG > \TS$ \footnote{However, we report the results for the Needle In Haystack family in the supplementary material. The results are unsurprising, where $\TS$ is the dominant strategy for both the entrant and incumbent.}. It seems clear that the temporary monopoly will get a larger market share regardless of what algorithm it plays, but is the incumbent incentivized to commit to $\TS$?

@@

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../competing_bandits"
%%% End:

>>>>

\documentclass[../competing_bandits.tex]{subfiles}
\begin{document}
\section{Competition vs Better Algorithms}\label{section:5}
\swedit{how about just name the section ``inverted U''?}  \swedit{Now
  we demonstrate the inverted-U relationship between the incentivized
  algorithms and the competition levels. In particular, we investigate
  the incentivized algorithms under three different regimes: permanent
  monopoly, temporary monopoly, and permanent duopoly. First, the
  story for permanent monopoly is relatively straightforward.}

@@

% couldn't get section references to work so hardcoding for now
We utilize the same instances and realizations as in the section 3  and simulate the model described in section 2. We initially take the strategies of the firms as exogenous (chosen from $\mathcal{A}$) and simulate the model given these strategies in order to determine the expected payoffs associated with each pair of algorithms. Unless otherwise noted, all the results are reported at $t = 2000$.

\xhdr{Permanent Monopoly} Under permanent monopoly only a single firm exists in the market for every period. In our model the firm only gets utility from a larger market share so it is indifferent between each algorithm in $\mathcal{A}$ since, regardless of the algorithm it deploys, it will get the entire market. If we suppose that deploying the ``better" algorithms has even an $\epsilon > 0$ cost or, equivalently, that firms break indifference towards algorithms that are easier to deploy, then the firm would choose to deploy $\DG$.
}

@@

\OMIT{
\begin{definition}
\textit{Effective End of Game (EEOG)} - the last round, $t$, in a simulation where the agent alive at $t-1$ and the agent alive at $t$ choose different firms.
\end{definition}
}
Since both firms enter at the same time the game is symmetric and we only need to compute the payoffs of three pairs of strategies. We do not report them in the figures, but when both firms play the same algorithm the expected market share is 50/50.

@@

\xhdr{Temporary Monopoly} We now consider asymmetries in the timing of entry so that one firm enters the market before the other and serves as a monopolist in the periods until the other firm enters. In terms of our model, this corresponds to varying the value of $X$. For this section we report results fixing $T_0 = 20$ and focus on the family of instances where we observed that, for this warm start, $\DG > \TS$ \footnote{However, we report the results for the Needle In Haystack family in the supplementary material. The results are unsurprising, where $\TS$ is the dominant strategy for both the entrant and incumbent.}. It seems clear that the temporary monopoly will get a larger market share regardless of what algorithm it plays, but is the incumbent incentivized to commit to $\TS$?

@@

\end{document}
